\chapter{Scope of Work}

This project was developed during industrial training at \textbf{Nityashree Infosystems Pvt. Ltd.} as a client-style internal operations management system for \textbf{Bharat Finvest}.

The project scope covered end-to-end lifecycle stages:

\textbf{1. Requirement Understanding}
\begin{itemize}[leftmargin=1.3cm]
\item Identify entities: users, employees, tasks, attendance.
\item Define role behaviors and API-level restrictions.
\item Define reporting requirements and demo credentials.
\end{itemize}

\textbf{2. Application Development}
\begin{itemize}[leftmargin=1.3cm]
\item Frontend implementation with React, Vite, Bootstrap.
\item Backend API implementation with Express and MySQL2.
\item JWT authentication and authorization middleware.
\end{itemize}

\textbf{3. Data Modeling}
\begin{itemize}[leftmargin=1.3cm]
\item Relational schema design for users, employees, tasks, attendance.
\item Seed dataset creation including employee and intern records.
\end{itemize}

\textbf{4. DevOps and Operations}
\begin{itemize}[leftmargin=1.3cm]
\item Docker Compose environment for frontend, backend, and MySQL.
\item Health check API and container health validation.
\item CI pipeline for backend import verification and frontend build.
\item Backup and restore scripts for database operations.
\end{itemize}

\textbf{5. QA and Stabilization}
\begin{itemize}[leftmargin=1.3cm]
\item Validation of all major UI actions and backend responses.
\item Error handling, confirmation prompts, and loading states.
\item Final data consistency verification for demo safety.
\end{itemize}

\textbf{Out of Scope Clarification}
\begin{itemize}[leftmargin=1.3cm]
\item Official production deployment and live organization roll-out are outside the current academic project scope.
\item No claim is made for official production adoption by Bharat Finvest in this report.
\end{itemize}
