\chapter{Database Design}

The database schema is defined in \texttt{database/schema.sql} and seeded through \texttt{database/seed.sql}.

\section{Tables}
\subsection*{1. users}
Stores authenticated application users.
\begin{itemize}[leftmargin=1.3cm]
\item Primary Key: \texttt{id}
\item Key fields: \texttt{name}, \texttt{email} (unique), \texttt{password\_hash}, \texttt{role}, \texttt{department}
\item Role values: \texttt{admin}, \texttt{manager}, \texttt{employee}
\end{itemize}

\subsection*{2. employees}
Stores employee and intern profile records.
\begin{itemize}[leftmargin=1.3cm]
\item Primary Key: \texttt{id}
\item Foreign Key: \texttt{user\_id} references \texttt{users(id)}
\item Unique field: \texttt{employee\_code}
\item Key fields: \texttt{name}, \texttt{email}, \texttt{phone}, \texttt{department}, \texttt{designation}, \texttt{date\_of\_joining}, \texttt{status}
\item Status values: \texttt{active}, \texttt{inactive}
\end{itemize}

\subsection*{3. tasks}
Stores tasks assigned to employees.
\begin{itemize}[leftmargin=1.3cm]
\item Primary Key: \texttt{id}
\item Foreign Keys: \texttt{assigned\_to} references \texttt{employees(id)}, \texttt{assigned\_by} references \texttt{users(id)}
\item Key fields: \texttt{title}, \texttt{description}, \texttt{priority}, \texttt{status}, \texttt{due\_date}
\item Priority values: \texttt{low}, \texttt{medium}, \texttt{high}
\item Status values: \texttt{pending}, \texttt{in\_progress}, \texttt{completed}
\end{itemize}

\subsection*{4. attendance}
Stores attendance logs per employee and date.
\begin{itemize}[leftmargin=1.3cm]
\item Primary Key: \texttt{id}
\item Foreign Key: \texttt{employee\_id} references \texttt{employees(id)}
\item Unique composite key: \texttt{(employee\_id, date)}
\item Status values: \texttt{present}, \texttt{absent}, \texttt{half\_day}, \texttt{leave}
\end{itemize}

\section{Relationship Notes}
\begin{itemize}[leftmargin=1.3cm]
\item One user may be linked to zero or one employee profile (\texttt{users} to \texttt{employees}).
\item One employee can have many tasks and many attendance records.
\item One admin/manager user can assign many tasks.
\item Cascade operations are handled carefully in APIs to avoid accidental data deletion in demo scenarios.
\end{itemize}

\section{Seed Data Highlights}
\begin{itemize}[leftmargin=1.3cm]
\item Demo users: Admin (Akshay Shinde), Manager (Pravin Shinde), Employee (Ritesh Bhate).
\item Employee table includes 8 regular employees and 4 interns (total 12 records).
\item Seed includes realistic tasks and attendance records for reporting and dashboard visualization.
\end{itemize}
