\chapter{Security Implementation}

\section{Authentication Security}
\begin{itemize}[leftmargin=1.3cm]
\item User authentication uses JSON Web Token (JWT).
\item Login credentials are validated against hashed passwords in database.
\item Access token is required in \texttt{Authorization: Bearer <token>} header for protected APIs.
\item Backend middleware verifies token signature and expiration.
\end{itemize}

\section{Password Security with bcrypt}
\begin{itemize}[leftmargin=1.3cm]
\item Passwords are not stored in plaintext.
\item \texttt{bcrypt.compare()} is used during login to verify entered password against stored hash.
\item Seeded demo accounts include pre-generated bcrypt hashes.
\end{itemize}

\section{Role-Based Access Control}
\begin{itemize}[leftmargin=1.3cm]
\item \texttt{authMiddleware} authenticates request and populates \texttt{req.user}.
\item \texttt{allowRoles(...)} middleware restricts access by role.
\item Examples:
  \begin{itemize}[leftmargin=1.1cm]
  \item Employee deactivation and task deletion are admin-only.
  \item Create/update employee/task/attendance are admin/manager-level actions.
  \end{itemize}
\end{itemize}

\section{Database and Query Security}
\begin{itemize}[leftmargin=1.3cm]
\item Backend uses \texttt{mysql2/promise} with parameterized queries.
\item Query placeholders prevent SQL injection on dynamic inputs.
\item Constraints such as unique keys and foreign keys protect data integrity.
\end{itemize}

\section{Client-Side Session Handling}
\begin{itemize}[leftmargin=1.3cm]
\item Token and user data are stored in localStorage for session continuity.
\item On app load, \texttt{/api/auth/me} refreshes user profile from backend.
\item Axios interceptor handles 401 responses by clearing local state and redirecting to login.
\end{itemize}

\section{Operational Security Hygiene}
\begin{itemize}[leftmargin=1.3cm]
\item \texttt{.env} is excluded from version control.
\item \texttt{node\_modules} and SQL backup dumps are ignored in \texttt{.gitignore}.
\item CORS origin is explicitly set to \texttt{http://localhost:5173} in backend app configuration.
\end{itemize}
