\chapter{Testing Strategies}

The project validation was performed using a layered testing strategy to improve reliability and demo safety.

\section{Unit-level Validation}
Full formal unit test suites are not yet introduced with Jest/Mocha; however, core logic was validated at function level through controlled API requests and deterministic input scenarios.

\textbf{Examples:}
\begin{itemize}[leftmargin=1.3cm]
\item Payload validation for employee/task/attendance controllers.
\item Duplicate handling paths (attendance duplicate entry, employee duplicate keys).
\item JWT middleware accept/reject flows.
\end{itemize}

\section{Integration Testing}
Integration testing focused on API-to-database behavior.
\begin{itemize}[leftmargin=1.3cm]
\item CRUD flows were tested against real MySQL schema.
\item Foreign key constraints were verified through valid/invalid references.
\item Dashboard and summary APIs were validated for aggregated SQL output.
\end{itemize}

\section{System Testing}
System testing validated end-to-end behavior from browser to database.
\begin{itemize}[leftmargin=1.3cm]
\item Login and protected routing.
\item Employee, task, and attendance operation sequence.
\item PDF generation in reports page.
\item Logout and stale session fallback behavior.
\end{itemize}

\section{UI/UX Testing}
UI testing was executed with focus on visible controls and modal flows.
\begin{itemize}[leftmargin=1.3cm]
\item All actionable buttons were verified for expected behavior.
\item Required fields and form validation states were checked.
\item Success/error banners were verified after API responses.
\item Loading states and disabled buttons were verified during requests.
\end{itemize}

\section{Build and Runtime Verification}
\begin{itemize}[leftmargin=1.3cm]
\item Backend import verification: \texttt{node -e "require('./src/app')"}
\item Frontend production build verification: \texttt{npm run build}
\item Health endpoint verification: \texttt{GET /api/health}
\item CI build verification in GitHub Actions pipeline.
\end{itemize}

\section{Regression Safety}
Changes for branding, avatar logic, and DevOps enhancements were validated to ensure no break in existing core modules:
\begin{itemize}[leftmargin=1.3cm]
\item Login module remains functional.
\item Dashboard metrics continue loading.
\item CRUD operations remain stable.
\item PDF exports continue generating non-empty documents.
\end{itemize}
