\chapter{Test Cases}

\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.16}
\newcolumntype{T}[1]{>{\raggedright\arraybackslash}p{#1}}
\footnotesize

\begin{longtable}{T{0.9cm}T{2.4cm}T{3.0cm}T{5.0cm}T{1.7cm}}
\toprule
\textbf{ID} & \textbf{Test Case} & \textbf{Input / Action} & \textbf{Expected Result} & \textbf{Status} \\
\midrule
\endhead
TC01 & Login success & Valid admin credentials & Redirect to dashboard with active session and sidebar user details. & Pass \\
TC02 & Login failure & Invalid password & Error alert shown for invalid credentials. & Pass \\
TC03 & Auth refresh & Existing JWT, app reload & \texttt{/api/auth/me} refreshes user and updates localStorage state. & Pass \\
TC04 & Employee list load & Open Employees page & Paginated data displayed with search and avatar initials. & Pass \\
TC05 & Add employee & Submit valid Add Employee form & New employee created, success banner shown, table refreshed. & Pass \\
TC06 & Edit employee & Update existing employee details & Employee updated, modal closes after success, table refreshed. & Pass \\
TC07 & Deactivate employee & Admin clicks Deactivate and confirms & Employee status changes to inactive with success banner. & Pass \\
TC08 & Task list filter & Apply status and priority filters & Task table shows matching filtered records only. & Pass \\
TC09 & Add task & Submit valid task form with assignee & Task created and visible in refreshed list. & Pass \\
TC10 & Edit task & Update task status or due date & Task updated while preserving relational links. & Pass \\
TC11 & Delete task & Admin confirms task deletion & Task removed from database and UI list. & Pass \\
TC12 & Mark attendance & Submit employee/date/status in modal & Attendance entry inserted and table refreshed. & Pass \\
TC13 & Duplicate attendance guard & Mark same employee/date twice & API returns conflict; UI displays error in modal. & Pass \\
TC14 & Attendance filters & Filter by employee and date range & Table updates with matching records. & Pass \\
TC15 & Employee PDF export & Click Export PDF in Reports page & Downloaded PDF contains employee rows and header. & Pass \\
TC16 & Task PDF export & Click Export PDF in Reports page & Downloaded PDF contains task data with timestamp. & Pass \\
TC17 & Attendance PDF export & Click Export PDF in Reports page & Downloaded PDF contains attendance summary table. & Pass \\
TC18 & Logout flow & Click sidebar logout button & Token and user are removed; route redirects to login. & Pass \\
TC19 & Health API success & GET \texttt{/api/health} with DB available & JSON response shows status OK and database connected. & Pass \\
TC20 & Unauthorized route & Call protected API without token & HTTP 401 JSON error response returned. & Pass \\
\bottomrule
\end{longtable}
\normalsize

\section*{Notes on Evidence Collection}
\begin{itemize}[leftmargin=1.3cm]
\item API responses were verified through browser-driven requests and backend logs.
\item Frontend behavior was verified with modal actions, alerts, and table refresh checks.
\item Build and import checks were also validated through command-line verification and CI workflow.
\end{itemize}
